Using Interactive Graphics to Visualize Evening Grosbeak Movement and Migration Patterns

### 2024-05-13 paper.qmd
images

<!-- ![Evening Grosbeak image](eg_pic.jpeg){width = "100"} -->
<!-- {.lightbox} -->
<img src="eg_pic.jpeg" alt="Evening Grosbeak image" width="400"/>

@@

<img src="egmap.jpeg" alt="Evening Grosbeak range map" width="400"/>

<!--<p><small><em>Figure 1. Evening Grosbeak range map by American Bird Conservatory</em></small></p> -->

>>>>

![Evening Grosbeak image](eg_pic.jpeg)
<!-- {.lightbox} -->
<!-- <img src="eg_pic.jpeg" alt="Evening Grosbeak image" width="400"/> -->

@@

<!-- <img src="egmap.jpeg" alt="Evening Grosbeak range map" width="400"/> -->
![Evening Grosbeak Range Map](egmap.jpeg)

<p><small><em>American Bird Conservatory</em></small></p>
